\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.35in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\name{Yimian Liu} % Your name
\address{i@yimian.xyz \\ https://iotcat.me \\ 607-391-5915 }

\begin{document}
\begin{rSection}{Education}
{\textbf{Cornell University}} \hfill{\textbf{Ithaca, NY}}
\\ Master of Engineering in Electrical and Computer Engineering; GPA: \textbf{3.85/4.00} \hfill{\em Aug. 2022 - Dec. 2023}
\\ Relevant coursework: Distributed Computing Principles, Fundamentals of Machine Learning, Embedded Operating System, Computer Networks, UNIX Tools and Scripting

{\textbf{University of Liverpool}} \hfill{\textbf{Liverpool, UK}}
\\ Bachelor of Engineering in Electrical and Electronics (Honor Degree); GPA: \textbf{3.83/4.00} \hfill{\em Sep. 2017 -- July 2021}
\\ Relevant coursework: C/C++ Programming, Software Engineering, Image Processing, Neural Networks
\end{rSection}

\begin{rSection}{Skills}
{\textbf{Languages:}} Python, C/C++, TypeScript/JavaScript, Java, HTML/CSS, PHP, Lua, Bash, SQL, Assembly
\\{\textbf{Frameworks:}} Kubernetes, Kafka, Nginx, Express, Flask, React, MySQL, Redis, MongoDB, Elasticsearch, Keras
\\{\textbf{Tools/Skills:}} Linux, Git, Docker, Node.js, TCP/UDP, AWS, ChatGPT, OOD, RESTful, GraphQL, CI/CD

\end{rSection}

\begin{rSection}{Projects}

{\bf Full-Stack Development and Management of High-Traffic Websites and Web Services}\hfill{\textbf{Ithaca, NY}}
\\{\em Individual Project}\hfill {\em April 2018 - Present}
\\ $ \bullet $Conceptualized, designed, and deployed various self-developed, purpose-specific websites and web services.
\\ $ \bullet $Utilized cutting-edge technologies like Gatsby, \textbf{ReactJS}, \textbf{Sass}, Bootstrap, WebSocket, and \textbf{JQuery} for building interactive and responsive front-ends for websites, using GA4 for data-driven performance tracking and user interaction analysis.
\\ $ \bullet $Efficiently handled back-end services using a mix of Node.js, \textbf{Express}, Python \textbf{Flask}, and \textbf{PHP}, showing flexibility and adaptability across different programming environments and requirements.
\\ $ \bullet $Integrated \textbf{MySQL}, \textbf{MongoDB}, and \textbf{Redis} for effective data management and high-speed data caching.
\\ $ \bullet $Created a highly popular public Random Image API using PHP, MySQL, and Redis, which has \textbf{over 90,000 visits} per day, demonstrating the ability to develop and manage high-performance web services.

{\bf Deployment and Orchestration of a Robust Kubernetes Infrastructure}\hfill{\textbf{Ithaca, NY}}
\\{\em Individual Project}\hfill {\em Jan. 2023 - Present}
\\ $ \bullet $Engineered a scalable Kubernetes infrastructure with Kubeadm and Helm, efficiently managing high-traffic web services.
\\ $ \bullet $Leveraged \textbf{Docker} for efficient application containerization, enhancing deployment across different environments.
\\ $ \bullet $Orchestrated Docker containers using \textbf{Kubernetes} for effective load balancing and auto-scaling.
\\ $ \bullet $Deployed \textbf{Nginx} Ingress to manage external service access, enhancing security and load distribution.
\\ $ \bullet $Utilized Prometheus and Grafana to monitor system performance and health, optimizing resource utilization and stability.
\\ $ \bullet $Established a centralized logging infrastructure using Elasticsearch, Logstash, Kibana (\textbf{ELK} Stack), and \textbf{Kafka}, thereby facilitating real-time log processing, comprehensive system monitoring, and efficient troubleshooting.
\\ $ \bullet $Integrated DroneCI and Github for \textbf{CI/CD}, enabling streamlined updates and efficient bug fixes.


{\bf Distributed, Linearizable, Sharded Key-Value Database}\hfill{\textbf{Ithaca, NY}}
\\{\em Course Project advised by Prof. Lorenzo Alvisi}\hfill {\em March 2023 - May 2023}
\\ $ \bullet $Designed and built a robust, sharded key-value store in \textbf{Java}, optimized for performance in distributed settings.
\\ $ \bullet $Implemented and modified the \textbf{Multi-Paxos} protocol, a crucial algorithm to guarantee the database system's resilience and continued operation, given a majority of servers remain functional.
\\ $ \bullet $Enhanced the system's functionality by streamlining the Multi-Paxos protocol into a simpler, more efficient \textbf{Raft}-like protocol, resulting in improved system performance and reduced complexity.
\\ $ \bullet $Employed a strategic approach to optimize the key-value store by incorporating sharding across server groups. Each group was designed to execute the Paxos consensus algorithm, thus ensuring system-wide consistency and reliability.

\end{rSection}

\begin{rSection}{Other Experience}

$ \bullet $\textbf{Machine Learning:} Secured \textbf{2nd rank} out of 55 in an in-class Kaggle competition at Cornell by architecting a highly accurate CNN model using \textbf{Keras}, with data preprocessing and ensembling techniques applied to a noisy MNIST dataset.
\\ $ \bullet $\textbf{Embedded Systems:} Built an access control system with \textbf{OpenCV} for facial recognition, Python \textbf{Multi-Processing}, touchscreen GUI, Raspberry Pi, servo, ensuring reliable user management, remote access control, and activity logging.
\\ $ \bullet $\textbf{Compiler and Network:} Developed SD-IoT Network Operating System (NOS) for NodeMCU, enabling JavaScript to Lua code compilation and supporting \textbf{TCP}, \textbf{UDP}, and \textbf{HTTP} protocols for seamless IoT control and interaction.
\\ $ \bullet $\textbf{IoT Systems:} Developed a reliable and secure smart home system with Arduino, ESP8266, CentOS7 server, mmWave Radar, and various sensors, incorporating \textbf{C/C++}, MQTT, OTA, and SMS notifications, operating safely for over 3 years.


\end{rSection}

\newpage

\end{document}